The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-20 paper/sections/results.tex
figures
fix image dimensions

@@

%multiple materials
\begin{figure}
  \includegraphics[width=\textwidth]{example-image-a}
  \caption{Avocado to show heterogenous materials}
  \label{fig:avocado}
\end{figure}

>>>>

\dave{use as many different meshes as possible for figures (i.e try not to have the same mesh show up in more than one figure if possible).}

@@

%different surface reps
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show subd simulation if we have it. If it works really well we'll just mix subds and nurbs throughout the paper. }
  \label{fig:subd}
\end{figure}

%editing example
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show input to simulation, show output then show output loaded in rhino/fusion 360 }
  \label{fig:edit}
\end{figure}

%multiple materials
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{Avocado to show heterogenous materials}
  \label{fig:avocado}
\end{figure}
